---
title: "PLZ und Einwohnerzahl In Deutschland"
author: "Achim Rumberger"
date: "14. Mai 2016"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
#rm(list=ls(all=TRUE))
library(choroplethr)
library(dplyr)
library(ggplot2)
library(rgdal)
library(maptools)
library(gpclib)
library(readr)
library(R6)
```
## Load the shape file into R
### Convert the resulting "SpatialPolygonsDataFrame"" into a standard "data.frame""


```{r, echo=FALSE}

ger_plz <- readOGR(dsn = "geo/plz-gebiete.shp/", layer = "plz-gebiete")

gpclibPermit()
#convert the raw data to a data.frame as ggplot works on data.frames
ger_plz@data$id <- rownames(ger_plz@data)
ger_plz.point <- fortify(ger_plz, region="id")
ger_plz.df <- inner_join(ger_plz.point,ger_plz@data, by="id")

# variable name 'region' is needed for choroplethr
ger_plz.df$region <- ger_plz.df$plz
```
## Load the stat data
```{r}
df <- read_csv("de_plz_einwohner.csv")
```
### See if the conversion was successful
```{r}
head(ger_plz.df)
```
### Plot the shapefile with ggplot2
```{r, echo=FALSE}
ggplot(ger_plz.df, aes(long, lat, group=group )) + geom_polygon()
```
## Merge the shapefile data with the csv data
### subclass Ari's class
```{r}
GERPLZChoropleth <- R6Class("GERPLZChoropleth", 
                        inherit = choroplethr:::Choropleth,
                        public = list(
                          initialize = function(user.df) {
                            super$initialize(ger_plz.df, user.df)
                          }
                        )
)
```
### Instantiate new class with the csv data
```{r}
#choropleth needs these two columnames - 'region' and 'value'
colnames(df) = c("region", "value")
c <- GERPLZChoropleth$new(df)
```

### Plot the graph
```{r, echo=FALSE}
c$ggplot_polygon = geom_polygon(aes(fill = value), color = NA)
c$title = "Comparison of number of Inhabitants per Zipcode in Germany"
c$legend= "Number of Inhabitants per Zipcode"
c$set_num_colors(9)
c$render()
```

## 
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
